\lsection{Requirements}{requirements}

\subsection{Goals}

\begin{itemize}
    \item Anonymity: Pre-registration only requires a Twitter handle and an email address, none of which needs to be linked to your identity.
    \item Server coordination: The ceremony will be coordinated by a server, which will: \begin{itemize}
        \item Manage the contribution queue for the participants, supporting priority tiers.
        \item Ensure that only pre-registered participants with valid signatures are allowed to take part in the ceremony.
        \item Ensure that no more than one participant is contributing at a given time.
        \item Ensure that no participant contributes more than once.
        \item Inform the participants about their queue/contribution status. 
        \item Check the validity proof of the proposed contributions before adding them to the ceremony.
        \item After a successful contribution, return its hash to the participant.
    \end{itemize}
    \item Updatable: More contributions can be added to the ceremony at later stages if desired.
    \item Verifiable: The ceremony and all its contributions can be verified by independent auditors. We ensure that is the case by:
    \begin{itemize}
        \item Publishing the transcript of the ceremony, including the validity proof and hash of each contribution.
        \item Asking participants to publish their hashes in independent locations, e.g. Twitter.
        \item Distributing an open-source verification library. 
    \end{itemize}
\end{itemize}

\subsection{Non-Goals}

\begin{itemize}
    \item Permisionless: We require participants to pre-register to contribute to the ceremony. However, registration is open to anyone with a Twitter account and an email address.
    \item Support for independently computed contributions: The ceremony only supports those contributions done through the server with our client. However, the server code is open-source and the transcript of the ceremony is publicly available for audits.
\end{itemize}